---
title: "Weight of Fish"
author: "Carolina"
date: "Fall 2021"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
```

# Predicting Fish Weight
```{r}
Perch<- filter(Fish,Species=="Perch")
Perch<-select(Perch,-Species)
```

## Perch

### Best Models
```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Perch,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

According to chart we can find the best models for predicting weight. According to this the best two regression models are height and width. The best overall model is Height.

### Best Two regressor model

According to this the best two regression models are height and width.

## Pike

```{r}
Pike<- filter(Fish,Species=="Pike")
Pike<-select(Pike,-Species)
```

### Best Models

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Pike,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

 According to chart we can find the best models for predicting weight. According to this the best two regression models are Length1 and Length3. The best overall model is Length3

### Best Two regressor model

```{r}
which.max(summary.out$adjr2)
```

## Roach
```{r}
Roach<- filter(Fish,Species=="Roach")
Roach<-select(Roach,-Species)
```

### Best Models

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Roach,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

 According to chart we can find the best models for predicting weight. According to this the best two regression models are Length3 and Width. The best overall model is Width by having a smaller subset size.

### Best Two regressor model

## Final Summary Statements

